[dcpo_demsupport]

### 2020-08-08 paper/dcpo_demsupport.Rmd
visualization of polarization

```{r dcpo-uncertainty, cache=TRUE}

@@

>>>>

```{r dcpo-uncertainty, eval = FALSE}

@@

```{r polarizationVisualization, eval = FALSE}
# Bootstrap to get confidence intervals

library(boot)

## function to obtain the mean
Bmean <- function(data, indices) {
  d <- data[indices] # allows boot to select sample 
    return(mean(d))
}

# bootstrapping with 1000 replications 
bootstrapCI_sigma <- function(aData) {
  aSigma <- aData$sigma
  result_temp <- boot(data = aSigma,
                      statistic = Bmean,
                      R = 1000) %>%
    boot.ci(type = "bca")
  tibble(
    mean = mean(aSigma),
    conf.low = result_temp$bca[4],
    conf.high = result_temp$bca[5]
  )
}

df_sigma <- purrr::map(1:1000, function(anEntry) {
  dcpo_sigma$sigma[anEntry, , ] %>%
  reformat_dcpo_output("sigma")
})

df_sigma_us <- map_df(df_sigma, function(aCountry){
  filter(aCountry, country == "United States")
})

df_sigma_usCI <- map_df(unique(df_sigma_us$year), function(aYear){
  dataAYear <- filter(df_sigma_us, year == aYear)
  bootstrapCI_sigma(dataAYear)
}) %>% 
  mutate(year = unique(df_sigma_us$year))

df_sigma_2019 <- map_df(df_sigma, function(aCountry){
  filter(aCountry, year == 2019)
})

df_sigma_2019CI <- map_df(unique(df_sigma_2019$country), function(aCountry){
  dataACountry <- filter(df_sigma_2019, country == aCountry)
  bootstrapCI_sigma(dataACountry)
}) %>% 
  mutate(country = unique(df_sigma_2019$country))

plot_us <- ggplot(df_sigma_usCI, aes(x = mean, y = year, xmin = conf.low, xmax = conf.high)) +
  geom_point() +
  geom_errorbarh(height=.2) + 
  scale_y_reverse(breaks = unique(df_sigma_us$year)) +
  xlab(expression("Polarization Estimates, "~sigma)) + 
  ggtitle("Polarization of the U.S. from 1988--2020") +
  theme_minimal() +
  theme(axis.title.y = element_blank())

plot_2019 <- ggplot(df_sigma_2019CI, aes(x = mean, y = country, xmin = conf.low, xmax = conf.high)) +
  geom_point() +
  geom_errorbarh(height=.2) + 
  xlab(expression("Polarization Estimates, "~sigma)) + 
  ggtitle("Polarization around the World in 2019") +
  theme_minimal() +
  theme(axis.title.y = element_blank())

gridExtra::grid.arrange(plot_us, plot_2019, nrow = 1)
```
